Identification of protoneutron star g-modes in gravitational-wave data

### 2020-09-09 results.tex
add new plots

To better quantity how well we reconstruct the ratio, we have also considered $\Delta$ the mean
over the track of the relative error of $r_i$.

@@

$\Delta$ values of each of the 100 noise realisation are shown as well as function of the distance
on Figure \ref{fig:s20results}. For a source located up to $\sim$\unit[10]{kpc} the relative error
remains smaller than 20\%. At small distance $\Delta$ is small but not null. This reflects the
approximation of the model used for $r$.
It is nevertheless remarkable that one can reconstruct the ratio time series with a good
precision at distance up to $\sim$ 10 kpc for this particular waveform. We have tested
that the method does not depend on features of {\texttt s20S} using 7 other waveforms
described in section \ref{sec:simulations} covering a large range of progenitor masses.
Figure \ref{fig:aLIGOall} shows that apart {\tt s11.2--LS220}, the ratio is well
reconstructed for all waveforms up to $\sim$ 10kpc.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_allwvfs}
 \caption{Median of $coverage$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. } \label{fig:aLIGOall}
\end{figure}

@@

    Simulation & \texttt{s11} & \texttt{s15} & \texttt{s15S} & \texttt{s15G} & \texttt{s20} & \texttt{s20S} & \texttt{s25}  & \texttt{s40}
    \\   
    \hline
    aLIGO      & 19.5         & 55.4         & 59.0          &   60.0        & 34.3         &   35.8          & 116.5         & 98.5
    \\ 
    \hline
    CE2
    \\
    \hline
    ET-B
    \\ 
  \end{tabular}
  \caption{%%
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors considered in this study. The source is located
    at 10 kpc and is optimally oriented with respect to the detector.
    %%
  }
  \label{Tab:SNR}
\end{table}

>>>>

To better quantify how well we reconstruct the ratio, we have also considered $\Delta$ the mean
over the track of the relative error of $r_i$.

@@

$\Delta$ values of each of the 100 noise realisation are shown as well as function of the distance
on Figure \ref{fig:s20results}. For a source located up to $\sim$\unit[10]{kpc} the relative error
remains smaller than 20\%. At small distance $\Delta$ is small but not null. This reflects the
approximation of the model used for $r$.
It is nevertheless remarkable that one can reconstruct the ratio time series with a good
precision at distance up to $\sim$ 10 kpc for this particular waveform, with $coverage$ value
larger than 80\%.
We have tested that the method does not depend on features of {\texttt s20S} using 7 other waveforms
described in section \ref{sec:simulations} covering a large range of progenitor masses.
Figure \ref{fig:aLIGO_cov_allwvf} shows that apart {\tt s11.2--LS220}, the ratio is well
reconstructed for all waveforms up to $\sim$ 10kpc. On this figure we also show the $coverage$
value in case of absence of signal. The median value is significantly different from 0 because
the g-mode reconstruction algorithm is looking for a continuously frequency increasing track
in the spectrogram, starting between 0 and 200 Hz. In Table \ref{tab:} we are reporting the
distance at which $coverage$ median is lower than 80\%.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_cov_allwvfs}
 \caption{Median of $coverage$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. The ``no signal'' line and band show the median and first and third quartile of $coverage$ in absence of any signal.} \label{fig:aLIGO_cov_allwvf}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_prec_allwvfs}
 \caption{Median of $Delta$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. The ``no signal'' line and band show the median and first and third quartile of $Delta$ in absence of any signal.} \label{fig:aLIGO_prec_allwvf}
\end{figure}

@@

    Simulation & \texttt{s11} & \texttt{s15} & \texttt{s15S} & \texttt{s15G} & \texttt{s20} & \texttt{s20S} & \texttt{s25}  & \texttt{s40}
    \\   
    \hline
    aLIGO char. distance & 7     &            &                &               &   15.6           &    11.3   &  8.9             &  11.5
    \\ 
    \hline
    SNR in aLIGO         & 19.5 & 55.4        & 59.0          &   60.0        & 34.3         &   35.8          & 116.5         & 98.5
    \\
    \hline
    \hline
    CE2  max. distance  &      &            &                &               &              &                 &               & 
    \\
    \hline
    SNR in CE2      &      &            &                &               &              &                 &               &
    \\
    \hline
    \hline
  \end{tabular}
  \caption{%%
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors considered in this study. The source is located
    at 10 kpc and is optimally oriented with respect to the detector.
    %%
  }
  \label{Tab:results}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/s20--SFHo_all3G}
  \caption{Median of $coverage$ for s20.0--SFHo CCSN waveform embedded in 3G detectors noise and located at different distance from the Earth. } \label{fig:s20--SFHo_all3G}
\end{figure}
